---
title: "tidySCE - part of tidytranscriptomics"
output: github_document
always_allow_html: true
---

<!-- badges: start -->
[![Lifecycle:maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing) [![R build status](https://github.com/stemangiola/tidySCE/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/stemangiola/tidySCE/actions)
<!-- badges: end -->

```{r echo=FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/")
```

**Brings SingleCellExperiment to the tidyverse!** 

Website: [tidySCE](https://stemangiola.github.io/tidySCE/articles/introduction.html)

Please also have a look at 

- [tidyseurat](https://stemangiola.github.io/tidyseurat/) for tidy manipulation of Seurat objects
- [tidybulk](https://stemangiola.github.io/tidybulk/) for tidy bulk RNA-seq data analysis
- [nanny](https://github.com/stemangiola/nanny) for tidy high-level data analysis and manipulation 
- [tidygate](https://github.com/stemangiola/tidygate) for adding custom gate information to your tibble 
- [tidyHeatmap](https://stemangiola.github.io/tidyHeatmap/) for heatmaps produced with tidy principles


```{r include=FALSE}
# Set path to plotly screenshot
screenshot <- "man/figures/plotly.png"
```


```{r child="man/fragments/intro.Rmd"} 
```